---
title: "SimulationAnalysis"
author: "Nathan Shepherd"
date: "2/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)

SPidx = read.csv("../joined_dfs/sp500_joined_Closed_prices_interp.csv")
#unique (unlist (lapply (SPidx, function (x) which (is.na (x)))))
#X = na.exclude(SPidx)

rows = SPidx[,1]
dates = SPidx[,2] 
X = SPidx[,!(names(SPidx) %in% c("X","Date"))]

plot(rows, X[,1])
plot(rows, X[,2])
```

```{r}
dividends = 1 / X
plot(rows, dividends[,2])
plot(rows, dividends[,1])
```

## Simulate 

> The expected return value growth R(t)

```{r}
prev_day = read.csv("../joined_dfs/rolled/sp500_joined_Closed_prices_roll1.csv")
rows = SPidx[,1]
dates = SPidx[,2] 
prev_day = prev_day[,!(names(prev_day) %in% c("X","Date"))]

# R(t + 1) = [ P(t)+D(t)-P(t-1) ] / P(t-1)
R = (X + dividends - prev_day) / prev_day
#write.csv(R, file="sp500_R.csv")

ggplot(R, aes(x = rows, y = R[,1])) + geom_point()

R_desc = read.csv("sp500_R_describe_cols.csv")

R_Sn_means = as.numeric(as.vector(R_desc[2,]))
ggplot(as.data.frame(R_Sn_means), aes(x = R_Sn_means)) + geom_density(fill = "blue", alpha = 0.25) + ggtitle("Mean of 2000 samples Sn")
```


```{r}
R_mu = read.csv("sp500_R_rowmean.csv")
ggplot(R_mu, aes(x = X, y = R_mu[,2])) + geom_point()

ggplot(data.frame(means = R_mu[,2]), aes(x = R_mu[,2])) + geom_density( fill = "green", alpha = 0.25) + ggtitle("Mean of Daily Return for SP500")

R_max = max(R_mu[,2])
R_min = min(R_mu[,2])
R_mean = mean(R_mu[,2])
R_sdev = sd(R_mu[,2])
```
## Note: Some statistics for the S&P500 mean of return
```{r}
R_desc_rowmean = read.csv("sp500_R_rowmean_describe_cols.csv")
R_desc_rowmean
```



# Simulate w ~ Uniform

```{r}
unif_means <- replicate(2000, {
  y = runif(500, min=R_min, max=R_max)
  mean(y)
})

# Uniform(min(R(t)), max(R(t))
ggplot(data.frame(means = unif_means) , aes(x = unif_means)) + geom_density(fill = "blue", alpha = 0.25) + ggtitle("Mean of 2000 samples with w ~ Uniform")
```



# Simulate w ~ Normal

```{r}
norm_means <- replicate(2000, {
  y = rnorm(500, mean=R_mean, sd=R_sdev)
  mean(y)
})

# Normal(mean(R_mu), sigma(R_mu))
ggplot(data.frame(means = norm_means), aes(x = norm_means)) + geom_density(fill = "blue", alpha = 0.25) + ggtitle("Mean of 2000 samples with w ~ Normal")
```


# Simulate w ~ Poisson

```{r}
pois_means <- replicate(2000, {
  y = rpois(500, lambda=R_mean)
  mean(y)
})

# Poisson(lambda = mean(R_mu))
ggplot(data.frame(means = pois_means), aes(x = pois_means)) + geom_density(fill = "blue", alpha = 0.25) + ggtitle("Mean of 2000 samples with w ~ Poisson")
```


# Analysis of E(R(t - h))

```{r}
exp_return = c(R_mu[,2])

for (i in 2:(length(R_mu[,2]))) {
  exp_return[i] = R_mu[i,2] + exp_return[i-1]
}
plot(exp_return, type='l')


sample_Sn = sample(R, 100)
sample_return = c(sum(sample_Sn[1,], na.rm = TRUE))
for (i in 2:(length(sample_Sn[,1]))) {
  alpha = as.numeric(as.vector(sample_Sn[i,]))
  
  sample_return[i] = sum(alpha, na.rm = TRUE) + sample_return[i-1]
}
plot(sample_return, type='l')
```



```{r}
#growth = function(start, time, Sn) {
#  sum(start * Sn[time,], na.rm = TRUE)
#}

#n = length(R[,1])
#init_inv = 1000 # Dollars
#inv_per_stock = init_inv / length( R[1,] )

#equity = c(sum(inv_per_stock * R[1,], na.rm = TRUE))
#for (i in 2:n) {
#  equity[i] = sum(equity[i-1] * R[i,], na.rm = TRUE)
#}
#plot(1:n, equity)
```
# Analysis: 
- What is the E[R(t)]?
  Assume the starting investment is worth $1000. 
  Distribute this equity across SP500 and record terminal worth.
  Simulate selecting Sn = 10000 and record terminal worth
- Distribute $1000 equity into portfolio of 490 stocks
- Compare returns over different timescales
```{r}
library(ggplot2)
X = read.csv("exp_equity_n_days_sp500.csv")[,2:5]
#hist(X[,1])

ggplot(data.frame(means = X[,1]), aes(x = X[,1])) + geom_density(fill = "purple", alpha = 0.25) + ggtitle("Simulated E[R] for Buy and Hold (7 days)")

ggplot(data.frame(means = X[,2]), aes(x = X[,2])) + geom_density(fill = "purple", alpha = 0.25) + ggtitle("Simulated E[R] for Buy and Hold (90 days)")

ggplot(data.frame(means = X[,3]), aes(x = X[,3])) + geom_density(fill = "purple", alpha = 0.25) + ggtitle("Simulated E[R] for Buy and Hold (1 year)")

ggplot(data.frame(means = X[,4]), aes(x = X[,4])) + geom_density(fill = "purple", alpha = 0.25) + ggtitle("Simulated E[R] for Buy and Hold (2 years)")
```
- Compare difference in E[R(t)] as equity
```{r}
# FROM HW7
library(boot)


sample_means <- replicate(1000, {
  mean(sample(X[,1], 100))
})

print("Simulated E[R] for 7 days")
t.test(sample_means, conf.level = 0.999)$conf.int

diff_means <- function(data, index) {
  x_mu = mean(data[index,2])
  y_mu = mean(data[index,1])
  x_mu - y_mu
}

print("Simulated difference in mean for 90days vs 7days")
dm_boot <- boot(X, diff_means, R = 1000)
(dm_boot_ci <- boot.ci(dm_boot, type = c('basic', 'perc')))
```
```{r}
sample_means <- replicate(1000, {
  mean(sample(X[,3], 100))
})

print("Simulated E[R] for 1 year")
t.test(sample_means, conf.level = 0.999)$conf.int

sample_means <- replicate(1000, {
  mean(sample(X[,4], 100))
})

print("Simulated E[R] for 2 years conf interval")
t.test(sample_means, conf.level = 0.999)$conf.int
```


- What is the distribution of w
  Use correlation and RSS as cost function
```{r}
set.seed(406)

# Estimating 7day expected return given w ~ Normal
n = length(X[,1])
Y = X[,1]
Y_mu = mean(Y)
Y_sd = sd(Y)
Y = as.data.frame(Y)
Y$norm = rnorm(n, Y_mu, Y_sd)
Y$pois = rpois(n, Y_mu)
Y$R = sample(R_mu[,2], n, replace = TRUE)
pairs(Y)
#x = data[index,]
#n_row = nrow(x)
smpl = sample.int(n, size=floor(.8*n), replace=F)
train = Y[smpl,]
test = Y[-smpl,]
  
norm_model = lm(Y ~ norm + R, data=train)
summary(norm_model)
res = mean(predict(norm_model, test)) - mean(test$Y)
```


```{r}
cv_normal_equity <- function(data, index) {
  xystar = data[index, ]
  modstar = lm(Y ~ norm + R, data=data)
  res = mean(predict(modstar, data[index,]))
  res - mean(data[index,1])
}

print("Simulated difference in expected equity given w ~ Normal")
cv_boot <- boot(Y, cv_normal_equity, R = 1000)
(cv_boot_ci <- boot.ci(cv_boot, type = c('basic', 'perc')))
```
```{r}
cv_pois_equity <- function(data, index) {
  xystar = data[index, ]
  modstar = lm(Y ~ pois + R, data=data)
  res = mean(predict(modstar, data[index,]))
  res - mean(data[index,1])
}

print("Simulated difference in expected equity given w ~ Normal")
cv_boot <- boot(Y, cv_pois_equity, R = 1000)
(cv_boot_ci <- boot.ci(cv_boot, type = c('basic', 'perc')))
```

- What is the distribution of w
- Generate the optimum parameters of w for E[R(t)]

- Compare strategy using "head and Shoulder"
- Compare strategy using moving average














